---
title: "Clinical trials in Finland"
date: "`r paste0('Updated: ', Sys.Date())`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    # theme: xxx-theme-xxx
    css: theme-neuro.css
    highlight: tango  # specifies the syntax highlighting style
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(flexdashboard)
library(DT)
# source("load_data.R") #
Keyword <- df$Study$ProtocolSection$ConditionsModule$KeywordList$Keyword
Keyword[sapply(Keyword, is.null)] <- ""
dat <- dplyr::tibble(
    Status = as.factor(df$Study$ProtocolSection$StatusModule$OverallStatus),
    Title = df$Study$ProtocolSection$IdentificationModule$BriefTitle, 
    Organization = df$Study$ProtocolSection$IdentificationModule$Organization$OrgFullName, 
    Started = df$Study$ProtocolSection$StatusModule$StartDateStruct$StartDate,
    Condition = rapply((df$Study$ProtocolSection$ConditionsModule$ConditionList$Condition), paste0, collapse = ", "),
    Keyword = rapply(Keyword, paste0, collapse = ", "),
    Link = df$Link
  )
```


Trials
=======================================================================

Row
-----------------------------------------------------------------------

### Trials

```{r}
valueBox(nrow(dat), icon = "fa-medkit")
```

### Organizations

```{r}
valueBox(length(unique(df$Study$ProtocolSection$IdentificationModule$Organization$OrgFullName)), icon = "fa-sitemap")
```

### Sponsors

```{r}
valueBox(length(unique(df$Study$ProtocolSection$SponsorCollaboratorsModule$LeadSponsor$LeadSponsorName)), icon = "fa-user")
```


<!-- ### example&&&&&Subjects -->

<!-- ```{r} -->
<!-- valueBox(22222, icon = "fa-users") -->
<!-- ``` -->

Row
-----------------------------------------------------------------------


```{r datatable}
DT::datatable(dat,
              selection = c("single"),
              rownames = FALSE, 
              filter = 'top',
              escape = FALSE,
              #extensions = 'Buttons', 
              options = list(
                order = list(list(0, 'desc'), list(2, 'asc')),
                # dom = 'Bfrtip',
                search = list(regex = TRUE, caseInsensitive = TRUE),
                columnDefs = list(list(className = 'dt-left',  targets = "_all")),
                pageLength = 20
                # language = list(url = '//cdn.datatables.net/plug-ins/1.10.11/i18n/Finnish.json')
                # dom = 'Bfrtip',
                # buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
              )) 
# %>%
  # formatStyle(
  #   'Status',
  #   backgroundColor = styleEqual(levels = c("Not yet recruiting", "Recruiting", "Active, not recruiting"), values = c("yellow", "green", "orange"))
  # ) 
```

About
=======================================================================

### About this webpage

We collected information of the clinical trials which are currently held in Finland. Data is obtained from [ClinicalTrials.gov](https://clinicaltrials.gov/) and it is parsed, cleaned and formatted for user readable form. 

Search URL is defined so that trial location country is `Finland` and has one (or more) of the following criteria:

`Central Nervous System Diseases, Brain Diseases, Mental Disorders, Psychotic Disorders, Neurologic Manifestations, Cerebrovascular Disorders, Stroke, Quality of Life, Autoimmune Diseases of the Nervous System, Demyelinating Autoimmune Diseases, CNS, Demyelinating Diseases, Multiple Sclerosis, Behavioral Symptoms, Depression, Depressive Disorder, Neurocognitive Disorders, Neurodegenerative Diseases, Trauma, Nervous System, Alzheimer Disease, Dementia, Mood Disorders, Brain Ischemia, Brain Infarction, Craniocerebral Trauma, Muscular Diseases, Neuromuscular Diseases, Brain Injuries, Cerebral Infarction, Headache Disorders, Headache Disorders, Primary, Migraine Disorders, Tauopathies, Dyssomnias, Parasomnias, Sleep Disorders, Intrinsic, Sleep Wake Disorders, Intracranial Hemorrhages, Chemically-Induced Disorders, Aggression, Anxiety Disorders, Cognitive Dysfunction, Depressive Disorder, Major, Neurobehavioral Manifestations, Brain Injuries, Traumatic, Intracranial Aneurysm, Intracranial Arterial Diseases, Peripheral Nervous System Diseases, Schizophrenia, Schizophrenia Spectrum and Other Psychotic Disorders, Substance-Related Disorders, Brain Neoplasms, Subarachnoid Hemorrhage, Alcohol-Related Disorders, Cognition Disorders, Neurodevelopmental Disorders, Central Nervous System Neoplasms, Encephalomyelitis, Fatigue Syndrome, Chronic, Hydrocephalus, Ischemic Attack, Transient, Nervous System Neoplasms, Neuralgia, Paralysis, Sensation Disorders, Sleep Apnea Syndromes, Sleep Apnea, Obstructive, Spinal Cord Diseases, Alcohol Drinking, Alcoholism, Amnesia, Cataplexy, Communication Disorders, Disorders of Excessive Somnolence, Drinking Behavior, Narcolepsy, Sleep Initiation and Maintenance Disorders, Basal Ganglia Diseases, Brain Concussion, Brain Diseases, Metabolic, Brain Diseases, Metabolic, Inborn, Cerebral Hemorrhage, Cerebral Small Vessel Diseases, Fabry Disease, Fibromyalgia, Head Injuries, Closed, Hydrocephalus, Normal Pressure, Language Disorders, Meningitis, Movement Disorders, Multiple Sclerosis, Chronic Progressive, Multiple Sclerosis, Relapsing-Remitting, Parkinson Disease, Parkinsonian Disorders, Sphingolipidoses, Spinal Cord Injuries, Vision Disorders, Vision, Low, Behavior, Addictive, Burnout, Psychological, Conduct Disorder, Confusion, Delirium, Depression, Postpartum, Depressive Disorder, Treatment-Resistant, Developmental Disabilities, Disruptive, Impulse Control, and Conduct Disorders, Dyslexia, Dyspareunia, Enuresis, Gambling, Learning Disorders, Marijuana Abuse, Mutism, Nocturnal Enuresis, Occupational Stress, Problem Behavior, Psychological Trauma, Sleep Disorders, Circadian Rhythm, Stress Disorders, Traumatic, Stress, Psychological, Trauma and Stressor Related Disorders, Amyotrophic Lateral Sclerosis, Autonomic Nervous System Diseases, Bell Palsy, Brain Damage, Chronic, Brain Edema, Cerebral Palsy, Chronobiology Disorders, Complex Regional Pain Syndromes, Cranial Nerve Diseases, Deafness, Drug Resistant Epilepsy, Encephalitis, Epilepsy, Facial Injuries, Facial Nerve Diseases, Facial Paralysis, Headache Disorders, Secondary, Hearing Disorders, Hearing Loss, Hematoma, Subdural, Hematoma, Subdural, Chronic, Infratentorial Neoplasms, Intracranial Hemorrhage, Traumatic, Jaw Fractures, Mandibular Fractures, Maxillofacial Injuries, Meningitis, Meningococcal, Mononeuropathies, Motor Neuron Disease`

Check data [Terms and Conditions](https://clinicaltrials.gov/ct2/about-site/terms-conditions). In case of a question, please [contact us]().

