---
title: "Clinical trials in Finland"
date: "`r paste0('Updated: ', Sys.Date())`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    # theme: xxx-theme-xxx
    css: theme-neuro.css
    highlight: tango  # specifies the syntax highlighting style
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(flexdashboard)
library(DT)
# source("load_data.R") #
Keyword <- df$Study$ProtocolSection$ConditionsModule$KeywordList$Keyword
Keyword[sapply(Keyword, is.null)] <- ""
dat <- dplyr::tibble(
    Status = as.factor(df$Study$ProtocolSection$StatusModule$OverallStatus),
    Title = df$Study$ProtocolSection$IdentificationModule$BriefTitle, 
    Organization = df$Study$ProtocolSection$IdentificationModule$Organization$OrgFullName, 
    # Location = paste0(sapply(df$Study$ProtocolSection$ContactsLocationsModule$LocationList$Location, "[[", "LocationCity"), collapse = ", "),
    # Location = sapply(df$Study$ProtocolSection$ContactsLocationsModule$LocationList$Location, "[[", "LocationCity"),
    Started = df$Study$ProtocolSection$StatusModule$StartDateStruct$StartDate,
    Condition = rapply((df$Study$ProtocolSection$ConditionsModule$ConditionList$Condition), paste0, collapse = ", "),
    Keyword = rapply(Keyword, paste0, collapse = ", "),
    Link = df$Link
  )
```


Trials
=======================================================================

Row
-----------------------------------------------------------------------

### Trials

```{r}
valueBox(nrow(dat), icon = "fa-medkit")
```

### Organizations

```{r}
valueBox(length(unique(df$Study$ProtocolSection$IdentificationModule$Organization$OrgFullName)), icon = "fa-sitemap")
```

### Sponsors

```{r}
valueBox(length(unique(df$Study$ProtocolSection$SponsorCollaboratorsModule$LeadSponsor$LeadSponsorName)), icon = "fa-user")
```


<!-- ### example&&&&&Subjects -->

<!-- ```{r} -->
<!-- valueBox(22222, icon = "fa-users") -->
<!-- ``` -->

Row
-----------------------------------------------------------------------


```{r datatable}
DT::datatable(dat,
              selection = c("single"),
              rownames = FALSE, 
              filter = 'top',
              escape = FALSE,
              #extensions = 'Buttons', 
              options = list(
                order = list(list(0, 'desc'), list(2, 'asc')),
                # dom = 'Bfrtip',
                search = list(regex = TRUE, caseInsensitive = TRUE),
                columnDefs = list(list(className = 'dt-left',  targets = "_all")),
                pageLength = 20
                # language = list(url = '//cdn.datatables.net/plug-ins/1.10.11/i18n/Finnish.json')
                # dom = 'Bfrtip',
                # buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
              )) 
# %>%
  # formatStyle(
  #   'Status',
  #   backgroundColor = styleEqual(levels = c("Not yet recruiting", "Recruiting", "Active, not recruiting"), values = c("yellow", "green", "orange"))
  # ) 
```

About
=======================================================================

### About this webpage

We collected information of the clinical trials which are currently held in Finland. Data is obtained from [ClinicalTrials.gov](https://clinicaltrials.gov/) and it is parsed, cleaned and formatted for user readable form. 

Search URL is defined so that trial location country is `Finland` and has one (or more) of the following criteria:

`Central Nervous System Diseases, Brain Diseases, Lymphoma, Psychiatry, Autism, Mental Disorders, Psychotic Disorders, Neurologic Manifestations, Cerebrovascular Disorders, Stroke, Quality of Life, Endocrine Gland Neoplasms, Autoimmune Diseases of the Nervous System, Demyelinating Autoimmune Diseases, CNS, Demyelinating Diseases, Intracranial, Multiple Sclerosis, Neoplasms, Nerve Tissue, Neuroectodermal Tumors, Behavioral Symptoms, Neuroendocrine Tumors, Respiratory Tract Neoplasms, Depression, Depressive Disorder, Neurocognitive Disorders, Neurodegenerative Diseases, Trauma, Nervous System, Alzheimer Disease, Dementia, ADHD, Mood Disorders, Brain Ischemia, Brain Infarction, Craniocerebral Trauma, Headache Disorders, Muscular Diseases, Neuromuscular Diseases, Sleep Disorders, Brain Injuries, Cerebral Infarction, Migraine Disorders, Tauopathies, Dyssomnias, Parasomnias, Sleep Wake Disorders, Head and Neck Neoplasms, Stress, Sleep Apnea, Chemically-Induced Disorders, Aggression, Anxiety Disorders, Cognitive Dysfunction, Neurobehavioral Manifestations, Brain Injuries, Traumatic, Peripheral Nervous System Diseases, Schizophrenia, Schizophrenia Spectrum and Other Psychotic Disorders, Substance-Related Disorders, Brain Neoplasms, Subarachnoid Hemorrhage, Glioma, Neoplasms, Neuroepithelial, Alcohol-Related Disorders, Cognition Disorders, Neurodevelopmental Disorders, Central Nervous System Neoplasms, Encephalomyelitis, Fatigue Syndrome, Chronic, Hydrocephalus, Ischemic Attack, Transient, Nervous System Neoplasms, Neuralgia, Paralysis, Sensation Disorders, Spinal Cord Diseases, Astrocytoma, Cervical Intraepithelial Neoplasia, Glioblastoma, Alcohol Drinking, Alcoholism, Amnesia, Cataplexy, Communication Disorders, Disorders of Excessive Somnolence, Drinking Behavior, Narcolepsy, Sleep Initiation and Maintenance Disorders, Basal Ganglia Diseases, Brain Concussion, Brain Diseases, Metabolic, Brain Diseases, Metabolic, Inborn, Cerebral Hemorrhage, Cerebral Small Vessel Diseases, Fabry Disease, Fibromyalgia, Head Injuries, Closed, Language Disorders, Meningitis, Movement Disorders, Parkinson Disease, Parkinsonian Disorders, Sphingolipidoses, Spinal Cord Injuries, Vision Disorders, Vision, Low, Cysts, Ganglion Cysts, Osteosarcoma, Behavior, Addictive, Burnout, Psychological, Conduct Disorder, Confusion, Delirium, Developmental Disabilities, Disruptive, Impulse Control, and Conduct Disorders, Dyslexia, Dyspareunia, Enuresis, Gambling, Learning Disorders, Marijuana Abuse, Mutism, Nocturnal Enuresis, Occupational Stress, Problem Behavior, Psychological Trauma, Trauma and Stressor Related Disorders, Amyotrophic Lateral Sclerosis, Autonomic Nervous System Diseases, Bell Palsy, Brain Damage, Chronic, Brain Edema, Cerebral Palsy, Chronobiology Disorders, Complex Regional Pain Syndromes, Cranial Nerve Diseases, Deafness, Drug Resistant Epilepsy, Encephalitis, Epilepsy, Facial Injuries, Facial Nerve Diseases, Facial Paralysis, Hearing Disorders, Hearing Loss, Hematoma, Infratentorial Neoplasms, Jaw Fractures, Mandibular Fractures, Maxillofacial Injuries, Meningitis, Meningococcal, Mononeuropathies, Motor Neuron Disease, Muscle Cramp, Muscular Atrophy, Neurocytoma, Neuromuscular Manifestations, Neurotoxicity Syndromes, Optic Nerve Diseases, Polyneuropathies, Primary Dysautonomias, Radiculopathy, Reflex Sympathetic Dystrophy, Sarcopenia, Sciatic Neuropathy, Sciatica, Seizures, Skull Fractures, Spasm, Speech Disorders`

Check data [Terms and Conditions](https://clinicaltrials.gov/ct2/about-site/terms-conditions). In case of a question, please [contact us]().

